Spin canonical divisors of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex
reword main corollary

\todo{I changed the following to incorporate the no odd weight case. Is it ok?}

The main theorem of this paper, Theorem ~\ref{thm:main}, combined with a result of Voight and
Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, together with Voight and Zureick-Brown ~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[9.3.1]{vzb:stacky} provide the following application
to modular forms. Note that the result from Voight and
Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately from the classical work of Kodaira--Spencer
\cite{kodaira-spencer:deformations}.

\begin{cor}
\label{cor:main-mod-forms}
Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
\ldots, e_r; \delta)$. 
If $M_k(\Gamma) = 0$ for all odd $k$, then $M(\Gamma)$ is generated in degree at most $3 \cdot\max(3,e_1,\ldots, e_r)$ with relations in degree at most $6 \cdot \max(3,e_1,\ldots, e_r)$.
If there is some odd $k$ for which $M_k(\Gamma) \neq 0,$ then, the ring of modular forms
$M(\Gamma)$ is
generated as a $\BC$-algebra by elements of degree at most $e = \max
 (5, e_1, \ldots , e_r)$ with relations in degree at most $2e,$ so long
as $\sigma$ does not lie in a finite list of exceptional cases, as
listed in Table ~\ref{table:g-1-exceptional} for signatures with $g
= 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g =
0$.
\end{cor}

>>>>

The main theorem of this paper, Theorem ~\ref{thm:main}, combined
with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
{vzb:stacky}, provides a statement on rings of modular forms.
Together with the main theorem from Voight and Zureick-Brown \cite
[Theorem 9.3.1]{vzb:stacky}, we have the following application to
rings of modular forms. Note that the lemma from Voight and Zureick-
Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
from the classical work of Kodaira--Spencer
\cite{kodaira-spencer:deformations}.

\begin{cor}
\label{cor:main-mod-forms}
Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
associated to $\Gamma \backslash \BH$ with signature $\sigma
= (g; e_1, \ldots, e_r; \delta)$.

If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
generated in degrees at most $6 \cdot \max(3, e_1,\ldots, e_r)$.

If there is some odd $k$ for which $M_k(\Gamma) \neq 0$, then the
ring of modular forms $M(\Gamma)$ is generated as a $\BC$-algebra
by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
e_r)$ so long as $\sigma$ does not lie in a finite list of
exceptional cases which are listed and described in Table
~\ref{table:g-1-exceptional} for signatures with $g = 1$ and in
Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
\end{cor}
